Flesh Simulation in the Field of Animation

### 2020-04-01 LaTeX-Master-Vorlage/chapter/Background.tex
background done, now paper

\todoredefined[inline]{
TODO: Check if all notations used later are declared.
}

@@

\subsection{Matrices}
In the upcoming chapters I will mainly be using matrices  in the calculations. This subsection lists an overview of the matrix properties used later:

\begin{property}[\textbf{Positive Definiteness}]
A matrix $\mathbf{A}$ is positive definite if $\mathbf{x}^\intercal \mathbf{Ax}$ is positive for all of the non-zero values of the column matrix $\mathbf{x}$.
\end{property}

\todoredefined[inline]{
TODO: Is this necessary?
}

@@

\begin{theorem}[\textbf{The SVD Theorem}]
\label{SVD}
Let $\mathbf{A}$ $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n. Then there exist orthogonal matrices $\mathbf{U}$ $\in$ $\mathbb{R}^{m x m}$, $\mathbf{V}$ $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\mathbf{\tilde{\Sigma}}$ $\in$ $\mathbb{R}^{m x n}$ such that
\begin{align*}
\mathbf{A} &= \mathbf{U \tilde{\Sigma} V^\intercal} \\
\mathbf{\tilde{\Sigma}} &= \left[ \begin{array}{cc} \mathbf{\Sigma} & 0 \\ 0 & 0 \end{array} \right]
\end{align*}
where $\mathbf{\Sigma}$ = diag ($\sigma_1$, $\sigma_2$, . . . , $\sigma_r$), and $\sigma_1$ $\geq$ $\sigma_2$ $\geq$ · · · $\geq$ $\sigma_r$ $>$ 0 are the positive singular values of $\mathbf{A}$.

\end{theorem}
The definition and theorem were taken from \cite{ford2014numerical} (def. \ref{SVD} S.113, thm. \ref{singular_values} S.300).

\todoredefined[inline]{
TODO: Check reference. Make paragraphs work together. Add examples.
}

@@

The definition and theorem were taken from \cite{Spencer1980} (thm. \ref{PD} S.12).

@@

\begin{definition}[\textbf{Frobenius Norm}]
\label{FN}
Let \textbf{A} be a (m $\times$ n) matrix in the real or complex space. Then the Frobenius norm is defined as 
\[
\| \mathbf{A} \|_{F} := \sqrt{\sum\limits_{i=1}^{m} \sum\limits_{j=1}^{n} |a_{ij}|^2}.
\]
\end{definition}

@@

\todoredefined[inline]{
TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/deformation_map}
	\caption{Deformation Map {\cite{STREAM2018}}}
	\label{fig:deformationmap}
\end{figure}

@@

\begin{wrapfigure}[10]{r}{5.5cm}
\centering
	\includegraphics[width=5.5cm]{resources/stretch_plot.png}
	\caption{Stretching of a rectangle}
	\label{stretch:1}
\end{wrapfigure} 
As an example, I am taking a simple deformation in 2D. Consider the coloured area in Fig. \ref{stretch:1}. We can stretch this area in the following way:
\begin{align*}
	\check{x} &= 1.5x + 0y		\\
	\check{y} &= 0x + 2y	
\end{align*}

@@

\subsection{Deformation Energy}
The deformation energy or strain energy $\Psi$ is a scalar that defines the stored energy of a object undergoing a deformation. The strain energy density is then the strain energy per unit volume. It equal to the work that has to be done by the stresses in order to alter the strains (\cite{KORSUNSKY20175}, p.10). This means that it is an indicator of how much force must be applied in order for an object to be deformed in a certain way. Thus we can use the deformation energy to express the relationship between the stresses and strains. We can illustrate this with a stress-strain curve shown in Fig. \ref{fig:stress_strain}. The area under the stress-strain curve corresponds to the strain energy.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/stress_strain_curve.png}
	\caption{Example for a stress-strain curve}
	\label{fig:stress_strain}
\end{figure}

@@

where $\epsilon_{11}$ is the lateral and $\epsilon_{22}$ the axial strain. The range in which $\sigma$ lies in starts at $-1$ and goes up to $0.5$ \cite{PhysRevB.80.132104}. Usually the poisson's ratio of a material is positive. A negative value would mean that the material becomes wider in the cross section when it is stretched. This behaviour is very uncommon in nature. Examples of materials with a negative poisson's ratio are for instance discussed in \textit{Foam structures with a negative Poisson's ratio} \cite{lakes1987foam} or \textit{Advances in negative Poisson's ratio materials} \cite{lakes1993advances}.

Here are some examples of the poisson's ratio of various materials:

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Material} & \textbf{Poisson's ratio} \\ \hline
    C (graphite) & 0.31 \\ \hline
    Sn (metal) & 0.357 \\ \hline
    Cu & 0.355 \\ \hline
    Zn & 0.25 \\ \hline
    Ag & 0.36 \\ \hline
    Au & 0.45 \\ \hline
    Concrete & 0.20–0.37 \\ \hline
    Titanium (dental alloy) & 0.30–0.31 \\ \hline
    Bronze & 0.34 \\ \hline
    18–8 Stainless steel & 0.305 \\ \hline
    Natural rubber & 0.4999 \\ \hline
	B\textsubscript{2}O\textsubscript{3} glass & 0.30 \\ \hline
	GeO\textsubscript{2} glass & 0.20 \\ \hline	
    \end{tabular}
    \caption{Different materials with their poisson's ratio taken from \cite{PhysRevB.80.132104}}
\label{table:1}
\end{table}

@@

\todoredefined[inline]{
TODO: Topic generally covered, maybe adjust the following:
Explain why volume preservation => high poisson's ratio. Explain how to get formula with lamé parameters, explain lamé parameters.
Explain more on negative poisson's value?
\\
Further reading: http://silver.neep.wisc.edu/~lakes/PoissonIntro.html
}

\todoredefined[inline]{
TODO: Add some exaples and visualisations. What exactly is it and what role does it play in a deformation process? Hyperelastic energy, connect with paper.
\\ To include: Piola-Kirchhoff Stress, Cauchy Green invariant, polar decomposition, cauchy green tensor
}

>>>>

@@

@@

\begin{theorem}[\textbf{The SVD Theorem}]
\label{SVD}
Let $\mathbf{A}$ $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n. Then there exist orthogonal matrices $\mathbf{U}$ $\in$ $\mathbb{R}^{m x m}$, $\mathbf{V}$ $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\mathbf{\tilde{\Sigma}}$ $\in$ $\mathbb{R}^{m x n}$ such that
\begin{align*}
\mathbf{A} &= \mathbf{U \tilde{\Sigma} V^\intercal} \\
\mathbf{\tilde{\Sigma}} &= \left[ \begin{array}{cc} \mathbf{\Sigma} & 0 \\ 0 & 0 \end{array} \right]
\end{align*}
where $\mathbf{\Sigma}$ = diag ($\sigma_1$, $\sigma_2$, . . . , $\sigma_r$), and $\sigma_1$ $\geq$ $\sigma_2$ $\geq$ · · · $\geq$ $\sigma_r$ $>$ 0 are the positive singular values of $\mathbf{A}$.
\end{theorem}

This definition and theorem were taken from \cite{ford2014numerical} (p.113, p.300).

@@

This theorem was taken from \cite{Spencer1980} (p.12).

@@

\begin{definition}[\textbf{Frobenius Norm}]
\label{FN}
Let \textbf{A} be a (m $\times$ n) matrix in the real or complex domain. Then the Frobenius norm is defined as 
\[
\| \mathbf{A} \|_{F} := \sqrt{\sum\limits_{i=1}^{m} \sum\limits_{j=1}^{n} |a_{ij}|^2}.
\]
\end{definition}

@@

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/deformation_map}
	\caption[Deformation Map]{Deformation Map {\cite{STREAM2018}}}
	\label{fig:deformationmap}
\end{figure}

@@

\begin{wrapfigure}[11]{r}{5.5cm}
\centering
	\includegraphics[width=5.5cm]{resources/stretch_plot.png}
	\caption[Stretching of a rectangle]{Stretching of a rectangle}
	\label{stretch:1}
\end{wrapfigure}
As an example, I am taking a simple deformation in 2D. Consider the coloured area in Fig. \ref{stretch:1}. We can stretch this area in the following way:
\begin{align*}
	\check{x} &= 1.5x + 0y		\\
	\check{y} &= 0x + 2y	
\end{align*}

@@

\subsection{Deformation Energy}
The deformation energy or strain energy $\Psi$ is a scalar that defines the stored energy of a object undergoing a deformation. The strain energy density is the strain energy per unit volume. It equal to the work that has to be done by the stresses in order to alter the strains (\cite{KORSUNSKY20175}, p.10). This means that the energy is an indicator of how much force must be applied in order for an object to be deformed in a certain way. Thus we can use the deformation energy to express the relationship between the stresses and strains. We can illustrate this with a stress-strain curve shown in Fig. \ref{fig:stress_strain}. The area under the stress-strain curve corresponds to the strain energy.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/stress_strain_curve.png}
	\caption[Stress-strain curve]{Example for a stress-strain curve\footnotemark}
	\label{fig:stress_strain}
\end{figure}
\footnotetext{https://commons.wikimedia.org/wiki/File:Stress-strain\_curve.svg}

@@

where $\epsilon_{11}$ is the lateral and $\epsilon_{22}$ the axial strain. The range in which $\sigma$ lies in starts at $-1$ and goes up to $0.5$ \cite{PhysRevB.80.132104}. Usually the poisson's ratio of a material is positive. A negative value would mean that the material becomes wider in the cross section when it is stretched. This behaviour is very uncommon in nature. Examples of materials with a negative poisson's ratio are for instance discussed in \textit{Foam structures with a negative Poisson's ratio} \cite{lakes1987foam} or \textit{Advances in negative Poisson's ratio materials} \cite{lakes1993advances}. In table \ref{table:1} are some examples of the poisson's ratio of various materials.

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Material} & \textbf{Poisson's ratio} \\ \hline
    C (graphite) & 0.31 \\ \hline
    Sn (metal) & 0.357 \\ \hline
    Cu & 0.355 \\ \hline
    Zn & 0.25 \\ \hline
    Ag & 0.36 \\ \hline
    Au & 0.45 \\ \hline
    Concrete & 0.20–0.37 \\ \hline
    Titanium (dental alloy) & 0.30–0.31 \\ \hline
    Bronze & 0.34 \\ \hline
    18–8 Stainless steel & 0.305 \\ \hline
    Natural rubber & 0.4999 \\ \hline
	B\textsubscript{2}O\textsubscript{3} glass & 0.30 \\ \hline
	GeO\textsubscript{2} glass & 0.20 \\ \hline	
    \end{tabular}
    \caption[Materials with their poisson's ratio]{Different materials with their poisson's ratio (\cite{PhysRevB.80.132104}, p. 3)}
\label{table:1}
\end{table}

@@

\todoredefined[inline]{
TODO: To include: Piola-Kirchhoff Stress
}

### 2020-04-01 LaTeX-Master-Vorlage/chapter/paper.tex
background done, now paper

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Symbol} & \textbf{Definition} \\ \hline
    $\mathbf{F} = \mathbf{RS}$ & Polar decomposition \\ \hline
    $J=\operatorname{det}(\mathbf{F})$ & Relative volume change \\ \hline
    $\mathbf{C}=\mathbf{F}^\intercal \mathbf{F}$ & Right Cauchy-Green  \\ \hline	
    $I_{C}=\operatorname{tr}(\mathbf{C})$ & First right Cauchy-Green invariant \\ \hline
    \end{tabular}
    \caption{Quantities derived from the Deformation Gradient \textbf{F}}
\label{table:gradient_quantities}
\end{table}

\todoredefined[inline]{
TODO: Check if everything is explained enough in Background.
}

\section{Energy Formulation}

\subsection{Stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. The focus of the authors was the deformation energy. In order to achieve a convincing result the first step is to specify some requirements. Firstly the energy has to be stable. More precisely, we need a hyperelastic energy that is stable in the following four important ways:

@@

\todoredefined[inline]{
TODO: Explain what last sentence means. Reference correct like this?
}

\begin{figure}[!ht]
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/inversion_1}  
  \caption{Rest state}
  \label{fig:inversion_1}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/inversion_2}  
  \caption{Zero-volume state}
  \label{fig:inversion_2}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  % include second image
  \includegraphics[width=.8\linewidth]{resources/inversion_3}  
  \caption{Inversed state}
  \label{fig:inversion_3}
\end{subfigure}
\caption{Inversion of a tetrahedron {\cite{STREAM2018}}}
\label{fig:inversion}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/meta_stability}
	\caption{Illustration of meta stability {\cite{STREAM2018}}}
	\label{fig:meta_stability}
\end{figure}

@@

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Energy} & \textbf{Author(s)} \\ \hline
    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ & e.g. Bonet and Wood 2008 \\ \hline
    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Wang and Yang 2016 \\ \hline
    \end{tabular}
    \caption{Summary of proposed energies (\cite{Smith:2018:SNF:3191713.3180491}, 12:3)}
\label{table:energies}
\end{table}

@@

\todoredefined[inline]{
TODO: Not all proofs and calculations included yet. Add or leave out some if too confusing.
}

@@

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step0.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step8.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step16.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step24.png}
        \caption{Stretch test on a hexahedral mesh}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step0.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step8.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step16.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step24.png}
        \caption{Stretch test on a tetrahedral mesh}
    \end{subfigure}
    \caption{Stretch test performed on a cube with (a) a hexahedral mesh and (b) a tetrahedral mesh}
    \label{fig:stretchtest}
\end{figure}

>>>>

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Symbol} & \textbf{Definition} \\ \hline
    $\mathbf{F} = \mathbf{RS}$ & Polar decomposition \\ \hline
    $J=\operatorname{det}(\mathbf{F})$ & Relative volume change \\ \hline
    $\mathbf{C}=\mathbf{F}^\intercal \mathbf{F}$ & Right Cauchy-Green  \\ \hline	
    $I_{C}=\operatorname{tr}(\mathbf{C})$ & First right Cauchy-Green invariant \\ \hline
    \end{tabular}
    \caption[Quantities derived from the Deformation Gradient]{Quantities derived from the Deformation Gradient \textbf{F}}
\label{table:gradient_quantities}
\end{table}

\section{Energy Formulation}
\subsection{Stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. The focus of the authors was the deformation energy. In order to achieve a convincing result the first step is to specify some requirements. Firstly the energy has to be stable. More precisely, we need a hyperelastic energy that is stable in the following four important ways:

@@

\todoredefined[inline]{
TODO: Explain what last sentence means.
}

\begin{figure}[!ht]
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/inversion_1}  
  \caption{Rest state}
  \label{fig:inversion_1}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/inversion_2}  
  \caption{Zero-volume state}
  \label{fig:inversion_2}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  % include second image
  \includegraphics[width=.8\linewidth]{resources/inversion_3}  
  \caption{Inversed state}
  \label{fig:inversion_3}
\end{subfigure}
\caption[Inversion of a tetrahedron]{Inversion of a tetrahedron {\cite{STREAM2018}}}
\label{fig:inversion}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/meta_stability}
	\caption[Illustration of meta stability]{Illustration of meta stability {\cite{STREAM2018}}}
	\label{fig:meta_stability}
\end{figure}

@@

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Energy} & \textbf{Author(s)} \\ \hline
    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ & e.g. Bonet and Wood 2008 \\ \hline
    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Wang and Yang 2016 \\ \hline
    \end{tabular}
    \caption[Summary of proposed energies]{Summary of proposed energies (\cite{Smith:2018:SNF:3191713.3180491}, 12:3)}
\label{table:energies}
\end{table}

@@

\todoredefined[inline]{
TODO: Not all proofs and calculations included. Add or leave out some if too confusing.
}

@@

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step0.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step8.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step16.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_step24.png}
        \caption{Stretch test on a hexahedral mesh}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step0.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step8.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step16.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_step24.png}
        \caption{Stretch test on a tetrahedral mesh}
    \end{subfigure}
    \caption[Stretch test performed on a cube]{Stretch test performed on a cube with (a) a hexahedral mesh and (b) a tetrahedral mesh}
    \label{fig:stretchtest}
\end{figure}
